true

### 2017-04-05 draft1.tex
try and fail

\documentclass[article]{jss}
\usepackage[utf8]{inputenc}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\author{
Ross Jacobucci\\University of Notre Dame
}
\title{\pkg{regsem}: Regularized Structural Equation Modeling}
\Keywords{regularization, structural equation modeling, latent variables, \proglang{R}}

\Abstract{
The \pkg{regsem} package in \proglang{R}, an implementation of
regularized structural equation modeling (RegSEM; Jacobucci, Grimm, and
McArdle 2016), was recently developed with the goal of incorporating
various forms of penalized likelihood estimation in a broad array of
structural equations models. The forms of regularization include both
the \textit{ridge} (Hoerl and Kennard 1970) and the least absolute
shrinkage and selection operator (\textit{lasso}; Tibshirani 1996),
along with sparser extensions. RegSEM is particularly useful for
structural equation models that have a small parameter to sample size
ratio, as the addition of penalties can reduce the complexity, thus
reducing the bias of the parameter estimates. The paper covers the
algorithmic details and an overview of the use of \pkg{regsem} with the
application of both factor analysis and latent growth curve models.
}

\Plainauthor{Ross Jacobucci}
\Plaintitle{regsem: Regularized Structural Equation Modeling}
\Shorttitle{\pkg{regsem}}
\Plainkeywords{regularization, structural equation modeling, latent variables, R}

%% publication information
%% \Volume{50}
%% \Issue{9}
%% \Month{June}
%% \Year{2012}
\Submitdate{}
%% \Acceptdate{2012-06-04}

\Address{
    Ross Jacobucci\\
  University of Notre Dame\\
  118 Haggar Hall, Notre Dame, IN 46556\\
  E-mail: \href{mailto:rcjacobuc@gmail.com}{\nolinkurl{rcjacobuc@gmail.com}}\\
  URL: rjacobucci.com\\~\\
  }

\usepackage{amsmath} \usepackage{float} \usepackage{algorithm}
\usepackage[noend]{algpseudocode} \usepackage[subnum]{cases}

\begin{document}

@@

for \(\gamma > 0\). As seen in Figure 2, this results in similar amount
of shrinkage for smaller estimates in comparison to the SCAD, however,
less for larger estimates. For both the SCAD and MCP, both the
\(\gamma\) and \(\lambda\) parameters are used as hyper-parameters. This
involves testing models over a two-dimensional array of parameters,
however, in \pkg{regsem}, \(\gamma\) is by default fixed to 3.7 per Fan
and Li (2001).

@@

RegSEM is implemented as the \pkg{regsem} package (Jacobucci 2017) in
the \proglang{R} statistical environment (R Core Team 2017). To estimate
the maximum likelihood fit of the model, \pkg{regsem} uses
\textit{Reticular Action Model} (RAM; McArdle and McDonald 1984; McArdle
2005) notation to derive an implied covariance matrix. The parameters of
each SEM are translated into three matrices: the \textit{filter}
(\textit{F}), the \textit{asymmetric} (\textit{A}; directed paths;
e.g.~factor loadings or regressions), and the \textit{symmetric}
(\textit{S}; undirected paths; e.g.~covariances or variances). See
Jacobucci, Grimm, and McArdle (2016) for more detail on RAM notation and
its application to RegsEm.

Syntax for using the \pkg{regsem} is based on the \pkg{lavaan} package
(Rosseel 2012) for structural equation models. \pkg{lavaan} is a general
SEM software program that can fit a wide array of models with various
estimation methods. To use \pkg{regsem}, the user has to first fit the
model in \pkg{lavaan}. Note that particularly in cases that the number
of variables is larger than the sample size, the model in lavaan does
not need to converge, let alone run. In this case, the
\code{do.fit=FALSE} argument in lavaan can be used. As a canonical
example, below is the code for a confirmatory factor analysis model with
one latent factor and nince indicators from the Holzinger and Swineford
(1939) dataset.

\begin{CodeChunk}
\begin{CodeInput}
library(lavaan)
mod <- "
f1 = ~ NA*x1 + x2 + x3 + x4 + x5 + x6 + x7 + x8 + x9
f1~~1*f1
"
out <- cfa(mod,HolzingerSwineford1939)
\end{CodeInput}
\end{CodeChunk}

After a model is run in lavaan, using \code{lavaan()} or any of the
wrapper functions for fitting a model (i.e. \code{sem()}, \code{cfa()},
or \code{growth()}), the object is then used by the regsem package to
translate the model into RAM notation and run using one of three
functions: \code{regsem()}, \code{multi_optim()}, or \code{cv_regsem()}.
The \code{regsem()} function runs a model with one penalty value,
whereas \code{multi_optim()} does the same but allows for the use of
random starting values. However, the main function is \code{cv_regsem()}
as this not only runs the model, but runs it across a vector of varying
penalty values. For instance in the above one-factor model, each of the
factor loadings can be tested with lasso penalties to determine whether
each indicator is a necessary component of the latent factor:

\begin{CodeChunk}
\begin{CodeInput}
library(regsem)
extractMatrices(out)["A"]
out.reg <- cv_regsem(out, type="lasso", 
                    pars_pen=c(1:9),n.lambda=15,jump=.05)
\end{CodeInput}
\end{CodeChunk}

In this, the function \code{extractMatrices()} allows the user to
examine at how the lavaan model is translated into RAM matrices.
Further, by looking at the \textit{A} matrix, the parameter numbers
corresponding to the factor loadings of interest for regularization can
be identified. For this model, the factor loadings represent parameter
numbers one through nine, of which we pass directly to the
\code{pars_pen} argument of the \code{cv_regsem()} function (if
\code{pars_pen=NULL} then all directed effects, outside of intercepts,
are penalized). Additionally, we pass the arguments of how many values
of penalty we want to test (\code{n.lambda=15}), how much the penalty
should increase for each model (\code{jump=.05}), and finally that lasso
estimation is used (\code{type="lasso"}).

The \code{out.reg} object contains two components, \code{out.reg[[1]]}
has the parameter estimates for each of the 15 models,

\begin{CodeChunk}
\begin{CodeInput}
head(round(out.reg[[1]],2),5)
\end{CodeInput}
\begin{CodeOutput}
     f1 -> x1 f1 -> x2 f1 -> x3 f1 -> x4 f1 -> x5 f1 -> x6 f1 -> x7
[1,]     0.51     0.26     0.25     0.98     1.08     0.92     0.20
[2,]     0.41     0.17     0.17     0.89     0.98     0.83     0.12
[3,]     0.33     0.10     0.10     0.83     0.91     0.77     0.06
[4,]     0.27     0.04     0.04     0.78     0.87     0.72     0.01
[5,]     0.21     0.00     0.00     0.75     0.83     0.69     0.00
     f1 -> x8 f1 -> x9 x1 ~~ x1 x2 ~~ x2 x3 ~~ x3 x4 ~~ x4 x5 ~~ x5
[1,]     0.20     0.31     1.10     1.31     1.21     0.38     0.49
[2,]     0.13     0.23     1.11     1.32     1.22     0.38     0.48
[3,]     0.08     0.17     1.13     1.33     1.23     0.38     0.47
[4,]     0.03     0.12     1.15     1.35     1.25     0.38     0.46
[5,]     0.00     0.07     1.18     1.37     1.26     0.39     0.46
     x6 ~~ x6 x7 ~~ x7 x8 ~~ x8 x9 ~~ x9
[1,]     0.36     1.15     0.98     0.92
[2,]     0.36     1.15     0.99     0.93
[3,]     0.36     1.16     1.00     0.94
[4,]     0.37     1.17     1.01     0.96
[5,]     0.38     1.18     1.02     0.97
\end{CodeOutput}
\end{CodeChunk}

while \code{out.reg[[2]]} contains information pertaining to the fit of
each model:

\begin{CodeChunk}
\begin{CodeInput}
round(out.reg[[2]],2)
\end{CodeInput}
\begin{CodeOutput}
      lambda conv rmsea     BIC
 [1,]   0.00    0  0.19 7805.18
 [2,]   0.05    0  0.19 7815.39
 [3,]   0.10    0  0.20 7840.40
 [4,]   0.15    0  0.21 7875.41
 [5,]   0.20    0  0.20 7885.68
 [6,]   0.25    0  0.21 7910.92
 [7,]   0.30    0  0.21 7933.99
 [8,]   0.35    0  0.22 7960.28
 [9,]   0.40    0  0.23 7990.80
[10,]   0.45    0  0.23 8007.95
[11,]   0.50    0  0.23 8034.00
[12,]   0.55    0  0.24 8069.15
[13,]   0.60    0  0.29 8360.53
[14,]   0.65    0  0.29 8360.53
[15,]   0.70    0  0.29 8360.51
\end{CodeOutput}
\end{CodeChunk}

@@

Instead of examining the \code{out.reg[[1]]} output matrix of parameter
estimates, users also have the option to plot the trajectory of each of
the penalized parameters. This is accomplished with
\code{plot_cv(out.reg,pars=1:9)}, resulting in:

\begin{CodeChunk}
\begin{CodeInput}
plot_cv(out.reg,pars=1:9)
\end{CodeInput}

\begin{center}\includegraphics{draft1_files/figure-latex/unnamed-chunk-6-1} \end{center}

\end{CodeChunk}

After a final model (penalty) is chosen, users have the option either
just use the output from \code{cv_regsem()}, or the final model can be
re-run with either \code{regsem()} or \code{multi_optim()} to attain
additional information. In the model above, the best fitting penalty,
according to the BIC, is \(\lambda=0\). However, for demonstration
purposes, we can choose a penalty of 0.2. With this, the model is re-run
with \code{regsem()}

\begin{CodeChunk}
\begin{CodeInput}
mod.out <- regsem(out, type="lasso", pars_pen=c(1:9),lambda=0.2)
#summary(mod.out)
\end{CodeInput}
\end{CodeChunk}

Note that the arguments used above correspond to the same arguments in
\code{multi_optim()}. However, \code{multi_optim()} has additional
optional arguments corresponding to the number or random starts to try.
Additional fit indices can be attained through the \code{fit_indices()}
function.

\begin{CodeChunk}
\begin{CodeInput}
fit_indices(mod.out)
\end{CodeInput}
\begin{CodeOutput}
$Data_Type
[1] "Train"

$fits
          Fmin         varFit              p          chisq        p.chisq 
       0.69087        0.00000        9.00000      415.90286        0.00000 
          nfac             df           npar              N baseline.chisq 
       1.00000       31.00000       14.00000      301.00000      918.85159 
   baseline.df           logl            ncp          rmsea    rmsea.lower 
      36.00000    -3903.04360        1.28301        0.20344        0.18598 
   rmsea.upper     rmsea.pval            CFI            TLI            BIC 
            NA        0.00000        0.56402        0.49370     7885.98674 
           AIC           CAIC         EBIC.5        EBIC.25 
    7834.08719     7983.11043     8051.12157     8017.06459 
\end{CodeOutput}
\end{CodeChunk}

These same fit measures can be accessed through \code{cv_regsem} through
changing the defaults with the \code{fit.ret=c("rmsea","BIC")} argument.
Finally, instead of assessing these fit indices on the same sample that
the models were run on, a holdout dataset could be used. This can be
done two ways: either with \code{cv_regsem(...,fit.ret2="test")} or with
\code{fit_indices(model,CV=TRUE,CovMat=)} and specifying the name of the
holdout covariance matrix.

Structural equation modeling is hard, and pairing with regularization
doesn't make it any easier. Given this, and the number of options
available in the \pkg{regsem} package, a Google group forum was created
in order to answer questions and trouble shoot at
\url{https://groups.google.com/forum/\#!forum/regsem}.

@@

To compare the different types of penalties in \pkg{regsem}, we return
to the the initial example of the latent growth curve model displayed in
Figure 1. Using the same simulated data, the model can be run in
\pkg{lavaan} as

\begin{CodeChunk}
\begin{CodeInput}
mod1 <- "
i =~ 1*x1 + 1*x2 + 1*x3 + 1*x4
s =~ 0*x1 + 1*x2 + 2*x3 + 3*x4
i ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8 + c9 + c10
s ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8 + c9 + c10
"
lav.growth <- growth(mod1,dat,fixed.x=T)
\end{CodeInput}
\end{CodeChunk}

Comparing different types of penalties in \pkg{regsem} requires a
different specification of the \code{type} argument. The options
currently include maximum likelihood (\code{"none"}), ridge
(\code{"ridge"}), lasso (\code{"lasso"}), adaptive lasso
(\code{"alasso"}), elastic net (\code{"enet"}), SCAD (\code{"scad"}),
and MCP (\code{"mcp"}). For the elastic net, there is an additional
hyperparameter, \(\alpha\) that controls the tradeoff between ridge and
lasso penalties. This is specified as \code{alpha=} , which has a
default of 0.5. Additionally, both the SCAD and MCP have the additional
hyper parameter of \(\gamma\), which is specified as \code{gamma=} and
defaults to 3.7 per Fan and Li (2001).

For the purposes of comparison, each of the 20 covariate regressions
were penalized using the lasso, adaptive lasso, SCAD, and MCP, and
compared to the maximum likelihood estimates. In this model, the data
were simulated to have two large effects (both \textit{c1} parameters),
two small effects (both \textit{c2} parameters) and sixteen true zero
effects (\textit{c3-c10} parameters). Note that the covariates were
simulated to have zero covariance among each variable. If there was
substantial collinearity among covariates, the elastic net would be more
appropriate to simultaneously select predictors while also accounting
for the collinearity. The parameter estimates corresponding the the best
fit of the BIC are has the fit of each model, resulting in Table 1,
created using the \pkg{xtable} package (Dahl 2009).

@@

This paper provides an introduction to the \pkg{regsem} package,
outlining the mathematical details of regularized structural equation
modeling (RegSEM; Jacobucci, Grimm, and McArdle 2016) and the usage of
the \pkg{regsem} package. RegSEM allows the use of regularization while
keeping the structural equation model intact, adding penalization
directly into the estimation of the model. The application of RegSEM was
detailed using two example models: a latent growth curve model with 20
predictors of both the latent intercept and slope, along with a factor
analysis with one latent factor. With the latent growth curve model, the
small parameter to sample size ratio resulted in a larger number of
false positives in using maximum likelihood estimation. In both the
simulated example and the small simulation, the different types of
regularization in \pkg{regsem} demonstrated better false positive and
negative rates in comparison to maxiumum likelihood across sample sizes.

Broadly speaking, there is a growing amount of research into the
integration between data mining methods and latent variable models.
Specifically, beyond RegSEM, this has taken the form of item response
theory and regularization (Sun et al. 2016), pairing both structural
equation models with decision trees (Brandmaier et al. 2013),
exploratory psychological network analaysis (e.g. Epskamp, Rhemtulla,
and Borsboom 2016), along with many others. The amount of pairing
between methods that have generally been housed in separate camps will
only increase into the future. This type of research will be facilitated
by the general upsurge in the creation of open source software that
gives users a general framework to test models. This was the motivation
behind creating the \pkg{regsem} package, in that users can estimate
models ranging from simple factor analysis models, to latent
longitudinal models with few to many time points, and finally to models
with a large number of latent and observed variables. The use of
regularization allows for the estimation of much larger structural
equation models than before. Specifically, given that latent variables,
as discussed in this article, are more commonly used in the social and
behavioral sciences, sample sizes are generally not large. To estimate
large models with small sample sizes invites increasing amounts of bias
as demonstrated with the simulated data in this paper. Regularization
can be used to reduce the complexity of the model, thus decreasing both
the bias and variance.

With highly constrained structural equation models, achieving model
convergence can be particularly problematic in using \pkg{regsem}. For
instance, with the latent change score model (McArdle and Hamagami
2001), Bayesian regularization methods have less difficulty in reaching
convergence across chains (Jacobucci and Grimm 2017). With the recent
advent of additional sparsity inducing priors, along with new forms of
software such as Stan (Carpenter et al. 2016), for some models it may be
more appropriate to use these Bayesian regularization methods over their
frequentist counterparts. In the realm of Bayesian regularization for
structural equation models, although some research exists (Feng, Wu, and
Song 2017), much more is warranted.

Future research with \pkg{regsem} should focus on a number of avenues.
One is comparing the different forms of regularization, delineating
which method may be best in which setting. Additionally, as structural
equation models become larger, with the advent of much larger datasets,
computational speed will become a principal concern. Although 40
penalties in the models tested above can be run in a matter of seconds
on a standard laptop, larger models can take much longer. To handle
this, future implementation with \pkg{regsem} will test the inclusion of
different types of optimization, specifically testing whether
computation of the Hessian (or approximate Hessian) can reduce the
number of optimization steps.

@@

This paper provided a brief overview on the use of the \pkg{regsem}
package as an implementation of regularized structural equation
modeling. Because structural equation modeling encompasses a wide array
of latent variable models, the \pkg{regsem} package was created as a
general package for including different forms of regularization into a
host of latent variable models. RegSEM, and thus the \pkg{regsem}
package, has been evaluated in a wide array of SEM models, including
confirmatory factor analysis (Jacobucci, Grimm, and McArdle 2016),
latent change score models (Jacobucci and Grimm 2017), mediation models
(Serang et al. in press). Future updates to \pkg{regsem} will focus on
decreasing the computational time of large latent variable models in
order to provide an avenue of testing for researchers collecting larger
and larger datasets. RegSEM is a method that operates at all ends of the
data size spectrum: allowing for a reduction in complexity when the
sample size is small, along with dimension reduction in the presence of
large data (both \(N\) and \(P\)).

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

@@

\end{document}

>>>>

% !TeX root = RJwrapper.tex
\title{true}
\author{by Ross Jacobucci}

\maketitle

\abstract{%
The \textbf{regsem} package in \textbf{R}, an implementation of
regularized structural equation modeling (RegSEM; Jacobucci, Grimm, and
McArdle 2016), was recently developed with the goal of incorporating
various forms of penalized likelihood estimation in a broad array of
structural equations models. The forms of regularization include both
the \textit{ridge} (Hoerl and Kennard 1970) and the least absolute
shrinkage and selection operator (\textit{lasso}; Tibshirani 1996),
along with sparser extensions. RegSEM is particularly useful for
structural equation models that have a small parameter to sample size
ratio, as the addition of penalties can reduce the complexity, thus
reducing the bias of the parameter estimates. The paper covers the
algorithmic details and an overview of the use of \textbf{regsem} with
the application of both factor analysis and latent growth curve models.
}

@@

for \(\gamma > 0\). As seen in Figure 2, this results in similar amount
of shrinkage for smaller estimates in comparison to the SCAD, however,
less for larger estimates. For both the SCAD and MCP, both the
\(\gamma\) and \(\lambda\) parameters are used as hyper-parameters. This
involves testing models over a two-dimensional array of parameters,
however, in \textbf{regsem}, \(\gamma\) is by default fixed to 3.7 per
Fan and Li (2001).

@@

RegSEM is implemented as the \textbf{regsem} package (Jacobucci 2017) in
the \textbf{R} statistical environment (R Core Team 2017). To estimate
the maximum likelihood fit of the model, \textbf{regsem} uses
\textit{Reticular Action Model} (RAM; McArdle and McDonald 1984; McArdle
2005) notation to derive an implied covariance matrix. The parameters of
each SEM are translated into three matrices: the \textit{filter}
(\textit{F}), the \textit{asymmetric} (\textit{A}; directed paths;
e.g.~factor loadings or regressions), and the \textit{symmetric}
(\textit{S}; undirected paths; e.g.~covariances or variances). See
Jacobucci, Grimm, and McArdle (2016) for more detail on RAM notation and
its application to RegsEm.

Syntax for using the \textbf{regsem} is based on the \textbf{lavaan}
package (Rosseel 2012) for structural equation models. \textbf{lavaan}
is a general SEM software program that can fit a wide array of models
with various estimation methods. To use \textbf{regsem}, the user has to
first fit the model in \textbf{lavaan}. Note that particularly in cases
that the number of variables is larger than the sample size, the model
in lavaan does not need to converge, let alone run. In this case, the
\textbf{do.fit=FALSE} argument in lavaan can be used. As a canonical
example, below is the code for a confirmatory factor analysis model with
one latent factor and nince indicators from the Holzinger and Swineford
(1939) dataset.

\begin{Schunk}
\begin{Sinput}
library(lavaan)
mod <- "
f1 = ~ NA*x1 + x2 + x3 + x4 + x5 + x6 + x7 + x8 + x9
f1~~1*f1
"
out <- cfa(mod,HolzingerSwineford1939)
\end{Sinput}
\end{Schunk}

After a model is run in lavaan, using \textbf{lavaan()} or any of the
wrapper functions for fitting a model (i.e. \textbf{sem()},
\textbf{cfa()}, or \textbf{growth()}), the object is then used by the
regsem package to translate the model into RAM notation and run using
one of three functions: \textbf{regsem()}, \textbf{multi_optim()}, or
\textbf{cv_regsem()}. The \textbf{regsem()} function runs a model with
one penalty value, whereas \textbf{multi_optim()} does the same but
allows for the use of random starting values. However, the main function
is \textbf{cv_regsem()} as this not only runs the model, but runs it
across a vector of varying penalty values. For instance in the above
one-factor model, each of the factor loadings can be tested with lasso
penalties to determine whether each indicator is a necessary component
of the latent factor:

\begin{Schunk}
\begin{Sinput}
library(regsem)
extractMatrices(out)["A"]
out.reg <- cv_regsem(out, type="lasso", 
                    pars_pen=c(1:9),n.lambda=15,jump=.05)
\end{Sinput}
\end{Schunk}

In this, the function \textbf{extractMatrices()} allows the user to
examine at how the lavaan model is translated into RAM matrices.
Further, by looking at the \textit{A} matrix, the parameter numbers
corresponding to the factor loadings of interest for regularization can
be identified. For this model, the factor loadings represent parameter
numbers one through nine, of which we pass directly to the
\textbf{pars_pen} argument of the \textbf{cv_regsem()} function (if
\textbf{pars_pen=NULL} then all directed effects, outside of intercepts,
are penalized). Additionally, we pass the arguments of how many values
of penalty we want to test (\textbf{n.lambda=15}), how much the penalty
should increase for each model (\textbf{jump=.05}), and finally that
lasso estimation is used (\textbf{type="lasso"}).

The \textbf{out.reg} object contains two components,
\textbf{out.reg[[1]]} has the parameter estimates for each of the 15
models,

\begin{Schunk}
\begin{Sinput}
head(round(out.reg[[1]],2),5)
\end{Sinput}
\begin{Soutput}
#>      f1 -> x1 f1 -> x2 f1 -> x3 f1 -> x4 f1 -> x5 f1 -> x6 f1 -> x7
#> [1,]     0.51     0.26     0.25     0.98     1.08     0.92     0.20
#> [2,]     0.42     0.17     0.16     0.90     0.99     0.83     0.11
#> [3,]     0.00     0.00     0.00     0.00     0.00     0.00     0.00
#> [4,]     0.00     0.00     0.00     0.00     0.00     0.00     0.00
#> [5,]     0.00     0.00     0.00     0.00     0.00     0.00     0.00
#>      f1 -> x8 f1 -> x9 x1 ~~ x1 x2 ~~ x2 x3 ~~ x3 x4 ~~ x4 x5 ~~ x5
#> [1,]     0.20     0.31      1.1     1.31     1.21     0.38     0.49
#> [2,]     0.11     0.22      1.1     1.31     1.21     0.38     0.49
#> [3,]     0.00     0.00      1.1     1.31     1.21     0.38     0.49
#> [4,]     0.00     0.00      1.1     1.31     1.21     0.38     0.49
#> [5,]     0.00     0.00      1.1     1.31     1.21     0.38     0.49
#>      x6 ~~ x6 x7 ~~ x7 x8 ~~ x8 x9 ~~ x9
#> [1,]     0.36     1.15     0.98     0.92
#> [2,]     0.36     1.15     0.98     0.92
#> [3,]     0.36     1.15     0.98     0.92
#> [4,]     0.36     1.15     0.98     0.92
#> [5,]     0.36     1.15     0.98     0.92
\end{Soutput}
\end{Schunk}

while \textbf{out.reg[[2]]} contains information pertaining to the fit
of each model:

\begin{Schunk}
\begin{Sinput}
round(out.reg[[2]],2)
\end{Sinput}
\begin{Soutput}
#>       lambda conv rmsea     BIC
#>  [1,]   0.00    0  0.19 7805.18
#>  [2,]   0.05    0  0.19 7816.88
#>  [3,]   0.10    0  0.43 9460.55
#>  [4,]   0.15    0  0.43 9460.55
#>  [5,]   0.20    0  0.43 9460.55
#>  [6,]   0.25    0  0.43 9460.55
#>  [7,]   0.30    0  0.43 9460.55
#>  [8,]   0.35    0  0.43 9460.55
#>  [9,]   0.40    0  0.43 9460.55
#> [10,]   0.45    0  0.43 9460.55
#> [11,]   0.50    0  0.43 9460.55
#> [12,]   0.55    0  0.43 9460.55
#> [13,]   0.60    0  0.43 9460.55
#> [14,]   0.65    0  0.43 9460.55
#> [15,]   0.70    0  0.43 9460.55
\end{Soutput}
\end{Schunk}

@@

Instead of examining the \textbf{out.reg[[1]]} output matrix of
parameter estimates, users also have the option to plot the trajectory
of each of the penalized parameters. This is accomplished with
\textbf{plot_cv(out.reg,pars=1:9)}, resulting in:

\begin{Schunk}
\begin{Sinput}
plot(out.reg,pars=1:9)
\end{Sinput}

\includegraphics{draft1_files/figure-latex/unnamed-chunk-6-1} \end{Schunk}

After a final model (penalty) is chosen, users have the option either
just use the output from \textbf{cv_regsem()}, or the final model can be
re-run with either \textbf{regsem()} or \textbf{multi_optim()} to attain
additional information. In the model above, the best fitting penalty,
according to the BIC, is \(\lambda=0\). However, for demonstration
purposes, we can choose a penalty of 0.2. With this, the model is re-run
with \textbf{regsem()}

\begin{Schunk}
\begin{Sinput}
mod.out <- regsem(out, type="lasso", pars_pen=c(1:9),lambda=0.2)
#summary(mod.out)
\end{Sinput}
\end{Schunk}

Note that the arguments used above correspond to the same arguments in
\textbf{multi_optim()}. However, \textbf{multi_optim()} has additional
optional arguments corresponding to the number or random starts to try.
Additional fit indices can be attained through the
\textbf{fit_indices()} function.

\begin{Schunk}
\begin{Sinput}
fit_indices(mod.out)
\end{Sinput}
\begin{Soutput}
#> $Data_Type
#> [1] "Train"
#> 
#> $fits
#>           Fmin         varFit              p          chisq        p.chisq 
#>        3.35383        0.00000        9.00000     2019.00407        0.00000 
#>           nfac             df           npar              N baseline.chisq 
#>        1.00000       36.00000        9.00000      301.00000      918.85159 
#>    baseline.df           logl            ncp          rmsea    rmsea.lower 
#>       36.00000    -4704.59420        6.61001        0.42850        0.41202 
#>    rmsea.upper     rmsea.pval            CFI            TLI            BIC 
#>             NA        0.00000       -1.24614       -1.24614     9460.55240 
#>            AIC           CAIC         EBIC.5        EBIC.25 
#>     9427.18840     9614.76378     9693.74446     9654.19442
\end{Soutput}
\end{Schunk}

These same fit measures can be accessed through \textbf{cv_regsem}
through changing the defaults with the \textbf{fit.ret=c("rmsea","BIC")}
argument. Finally, instead of assessing these fit indices on the same
sample that the models were run on, a holdout dataset could be used.
This can be done two ways: either with
\textbf{cv_regsem(...,fit.ret2="test")} or with
\textbf{fit_indices(model,CV=TRUE,CovMat=)} and specifying the name of
the holdout covariance matrix.

Structural equation modeling is hard, and pairing with regularization
doesn't make it any easier. Given this, and the number of options
available in the \textbf{regsem} package, a Google group forum was
created in order to answer questions and trouble shoot at
\url{https://groups.google.com/forum/\#!forum/regsem}.

@@

To compare the different types of penalties in \textbf{regsem}, we
return to the the initial example of the latent growth curve model
displayed in Figure 1. Using the same simulated data, the model can be
run in \textbf{lavaan} as

\begin{Schunk}
\begin{Sinput}
mod1 <- "
i =~ 1*x1 + 1*x2 + 1*x3 + 1*x4
s =~ 0*x1 + 1*x2 + 2*x3 + 3*x4
i ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8 + c9 + c10
s ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8 + c9 + c10
"
lav.growth <- growth(mod1,dat,fixed.x=T)
\end{Sinput}
\end{Schunk}

Comparing different types of penalties in \textbf{regsem} requires a
different specification of the \textbf{type} argument. The options
currently include maximum likelihood (\textbf{"none"}), ridge
(\textbf{"ridge"}), lasso (\textbf{"lasso"}), adaptive lasso
(\textbf{"alasso"}), elastic net (\textbf{"enet"}), SCAD
(\textbf{"scad"}), and MCP (\textbf{"mcp"}). For the elastic net, there
is an additional hyperparameter, \(\alpha\) that controls the tradeoff
between ridge and lasso penalties. This is specified as \textbf{alpha=}
, which has a default of 0.5. Additionally, both the SCAD and MCP have
the additional hyper parameter of \(\gamma\), which is specified as
\textbf{gamma=} and defaults to 3.7 per Fan and Li (2001).

For the purposes of comparison, each of the 20 covariate regressions
were penalized using the lasso, adaptive lasso, SCAD, and MCP, and
compared to the maximum likelihood estimates. In this model, the data
were simulated to have two large effects (both \textit{c1} parameters),
two small effects (both \textit{c2} parameters) and sixteen true zero
effects (\textit{c3-c10} parameters). Note that the covariates were
simulated to have zero covariance among each variable. If there was
substantial collinearity among covariates, the elastic net would be more
appropriate to simultaneously select predictors while also accounting
for the collinearity. The parameter estimates corresponding the the best
fit of the BIC are has the fit of each model, resulting in Table 1,
created using the \textbf{xtable} package (Dahl 2009).

@@

This paper provides an introduction to the \textbf{regsem} package,
outlining the mathematical details of regularized structural equation
modeling (RegSEM; Jacobucci, Grimm, and McArdle 2016) and the usage of
the \textbf{regsem} package. RegSEM allows the use of regularization
while keeping the structural equation model intact, adding penalization
directly into the estimation of the model. The application of RegSEM was
detailed using two example models: a latent growth curve model with 20
predictors of both the latent intercept and slope, along with a factor
analysis with one latent factor. With the latent growth curve model, the
small parameter to sample size ratio resulted in a larger number of
false positives in using maximum likelihood estimation. In both the
simulated example and the small simulation, the different types of
regularization in \textbf{regsem} demonstrated better false positive and
negative rates in comparison to maxiumum likelihood across sample sizes.

Broadly speaking, there is a growing amount of research into the
integration between data mining methods and latent variable models.
Specifically, beyond RegSEM, this has taken the form of item response
theory and regularization (Sun et al. 2016), pairing both structural
equation models with decision trees (Brandmaier et al. 2013),
exploratory psychological network analaysis (e.g. Epskamp, Rhemtulla,
and Borsboom 2016), along with many others. The amount of pairing
between methods that have generally been housed in separate camps will
only increase into the future. This type of research will be facilitated
by the general upsurge in the creation of open source software that
gives users a general framework to test models. This was the motivation
behind creating the \textbf{regsem} package, in that users can estimate
models ranging from simple factor analysis models, to latent
longitudinal models with few to many time points, and finally to models
with a large number of latent and observed variables. The use of
regularization allows for the estimation of much larger structural
equation models than before. Specifically, given that latent variables,
as discussed in this article, are more commonly used in the social and
behavioral sciences, sample sizes are generally not large. To estimate
large models with small sample sizes invites increasing amounts of bias
as demonstrated with the simulated data in this paper. Regularization
can be used to reduce the complexity of the model, thus decreasing both
the bias and variance.

With highly constrained structural equation models, achieving model
convergence can be particularly problematic in using \textbf{regsem}.
For instance, with the latent change score model (McArdle and Hamagami
2001), Bayesian regularization methods have less difficulty in reaching
convergence across chains (Jacobucci and Grimm 2017). With the recent
advent of additional sparsity inducing priors, along with new forms of
software such as Stan (Carpenter et al. 2016), for some models it may be
more appropriate to use these Bayesian regularization methods over their
frequentist counterparts. In the realm of Bayesian regularization for
structural equation models, although some research exists (Feng, Wu, and
Song 2017), much more is warranted.

Future research with \textbf{regsem} should focus on a number of
avenues. One is comparing the different forms of regularization,
delineating which method may be best in which setting. Additionally, as
structural equation models become larger, with the advent of much larger
datasets, computational speed will become a principal concern. Although
40 penalties in the models tested above can be run in a matter of
seconds on a standard laptop, larger models can take much longer. To
handle this, future implementation with \textbf{regsem} will test the
inclusion of different types of optimization, specifically testing
whether computation of the Hessian (or approximate Hessian) can reduce
the number of optimization steps.

@@

This paper provided a brief overview on the use of the \textbf{regsem}
package as an implementation of regularized structural equation
modeling. Because structural equation modeling encompasses a wide array
of latent variable models, the \textbf{regsem} package was created as a
general package for including different forms of regularization into a
host of latent variable models. RegSEM, and thus the \textbf{regsem}
package, has been evaluated in a wide array of SEM models, including
confirmatory factor analysis (Jacobucci, Grimm, and McArdle 2016),
latent change score models (Jacobucci and Grimm 2017), mediation models
(Serang et al. in press). Future updates to \textbf{regsem} will focus
on decreasing the computational time of large latent variable models in
order to provide an avenue of testing for researchers collecting larger
and larger datasets. RegSEM is a method that operates at all ends of the
data size spectrum: allowing for a reduction in complexity when the
sample size is small, along with dimension reduction in the presence of
large data (both \(N\) and \(P\)).

\bibliography{RJreferences}

@@

\address{%
Ross Jacobucci\\
University of Notre Dame\\
118 Haggar Hall, Notre Dame, IN 46556\\
}
\href{mailto:rcjacobuc@gmail.com}{\nolinkurl{rcjacobuc@gmail.com}}
